\section{\conclusiontitle}

\begin{frame}
\frametitle{\textbf{General conclusions}}
  % \begin{block}{\textbf{Conclusions}}
    \begin{itemize}[<+->]
    \item \textbf{The long term MFMP problem is presented}, 
      analyzed and compared with similar problems.
    \item \textbf{Several efficient solving approaches are implemented}
      MIP-based, metaheuristics, ML-based, and graph-based.
    \item \textbf{A functional desktop application was developed},
       deployed and validated successfully by Dassault Aviation on real datasets.
    \end{itemize}
\end{frame}

\begin{frame}
\frametitle{\textbf{Perspectives}}
  % \end{block}  
  % \pause
  % \begin{block}{\textbf{Perspectives}}
    \begin{itemize}[<+->]
      \item \textbf{Extend the problem} to include some additional secondary constraints.        
      \item \textbf{Integrate} novel techniques (ML and graph) inside known frameworks (CG, GRASP).
      \item \textbf{Generalize ML methodology}
        to obtain a probability distribution for patterns, automatize feature extraction.
      \item \textbf{Combine ML and VND},
        e.g., by applying learned-cuts during path-sampling to extract promising patterns.
    \end{itemize}
  % \end{block}
\end{frame}

\begin{frame}
\frametitle{\textbf{Journal articles}}

% \begin{block}{\textbf{}}

  \begin{itemize}
    \item F. Peschiera, R. Dell, J. Royset, A. Haït, N. Dupin, and O. Battaïa. A novel solution approach with ML-based pseudo-cuts for the Flight and Maintenance Planning problem. OR Spectrum, pages 1–30, jun 2020. ISSN 0171-6468. doi: 10.1007/s00291-020-00591-z.

    \item F. Peschiera, A. Haït, N. Dupin, and O. Battaïa. Long term planning of military aircraft flight and maintenance operations. Technical report, ISAE-SUPAERO, Université de Toulouse, France, 2020 (submitted).

    \item  F. Peschiera, N. Dupin, A. Haït, and O. Battaïa. Novel graph-based matheuristic to solve the flight and maintenance planning problem. Forthcoming (to be submitted).
  \end{itemize}

% \end{block}
\end{frame}

\begin{frame}
\frametitle{\textbf{Congress presentations}}
% \begin{block}{\textbf{}}

  \begin{itemize}
    \item F. Peschiera, A. Haït, N. Dupin, and O. Battaïa. Maintenance planning on french military aircraft operations. In Congrès annuel de la société Française de Recherche Opérationnelle et d’Aide à la Décision (ROADEF), pages 1–2, Lorient, FR, 2018.

    \item F. Peschiera, O. Battaïa, A. Haït, and N. Dupin. Bi-objective mip formulation for the  optimization of maintenance planning on french military aircraft operations. 2018. 
    
    \item F. Peschiera, A. Haït, N. Dupin, and O. Battaïa. A novel mip formulation for the optimization problem of maintenance planning of military aircraft. In XIX Latin-Iberoamerican Conference on Operations Research, Lima, PE, 2018
    
    \item F. Peschiera, N. Dupin, O. Battaïa, and A. Haït. An alternative mip formulation for the military flight and maintenance planning problem. In Congrès annuel de la société Française de Recherche Opérationnelle et d’Aide à la Décision (ROADEF), Montpellier, FR, 2020.

  \end{itemize}
% \end{block}

\end{frame}

