\section{\introtitle}

\begin{frame}
\frametitle{\textbf{Maintenance}}

  \begin{itemize}[<+->]
  \item
    Maintenance is costly.
  \item
    Complexity and durability needs are growing with time.

    \begin{itemize}[<+->]
    
    \item
      buildings that need to last 100 years.
    \item
      green energy needs lasting infrastructure.
    \end{itemize}
  \end{itemize}

\end{frame}

\begin{frame}
\frametitle{\textbf{Maintenance planning}}

  \begin{columns}[c]
    \column{0.5\linewidth}
    Three types:
    \pause
    \begin{itemize}[<+->]
      \setbeamercolor{alerted text}{fg=black} %change the font color
      \setbeamerfont{alerted text}{series=\bfseries} %make alerted text bold
      \item Corrective.
      \item \alert<5->{Preventive}.
      \item Predictive.
      % \only<1->{\item Corrective.}
      % \only<2-4>{\item Preventive.}
      % \onslide<5->{\item \textbf{Preventive}.}
      % \onslide<4->{\item Predictive.}
    \end{itemize} 

  \pause
  \column{0.5\linewidth}
  Three elements:

  \begin{itemize}[<+->]
    \item Tasks (planned over time).
    \item Resources (to do the tasks).
    \item Recovery tasks (to care for resources).
  \end{itemize}
  \end{columns}

\end{frame}

\begin{frame}
\frametitle{\textbf{Maintenance planning applications}}

  In production:
  \begin{itemize}[<+->]
    \item Tasks: scheduled jobs, product demand.
    \item Resources: machines, factories.
    \item Recovery tasks: setup times, refueling, maintenances.
  \end{itemize}  
  % \pause
  \onslide<5->{In transport: }
  \pause
  \begin{itemize}[<+->]
    \item Tasks: flights, train schedules, routes.
    \item Resources: aircraft, trains, vehicles.
    \item Recovery tasks: checks (=maintenances).
  \end{itemize}

\end{frame}

\begin{frame}[t]
\frametitle{\textbf{The Flight and Maintenance Planning (FMP) problem}}
  
  \begin{adjustbox}{max totalsize={\textwidth}{.5\textheight},center}
  \begin{tikzpicture}
    \input{graphs/FMP_example.tex} 
  \end{tikzpicture}
  \end{adjustbox}

  \begin{textblock*}{1.1\textwidth}(0.8cm, 7.5cm)
    \onslide<2->{
      \textbf{State of the art :} FMP
    }
    \begin{flushleft}
    % $\star$
    \onslide<2->{
      \citesize (1) C. Barnhart, N. L. Boland, L. W. Clarke, E. L. Johnson, G. L. Nemhauser, and R. G. Shenoi. Flight string models for aircraft fleeting and routing. Transportation Science, 1998.\\
    }
    \onslide<3->{
      \citesize (2) A. Sarac, R. Batta, and C. M. Rump. A branch-and-price approach for operational aircraft maintenance routing. European Journal of Operational Research, 2006.
    }
    \end{flushleft}
  \end{textblock*}
\end{frame}

\begin{frame}[t]
\frametitle{\textbf{The Military Flight and Maintenance Planning (MFMP) problem}}
  \begin{tikzpicture}
    \input{graphs/gantt_example_anim.tex}
  \end{tikzpicture}

  \begin{textblock*}{1.1\textwidth}(0.8cm, 8cm)
    \begin{flushleft}
    % $\star$
    \onslide<3->{
      \citesize $\star$ R. A. Hahn and A. M. Newman. Scheduling United States Coast Guard helicopter deployment and maintenance at Clearwater Air Station, Florida. Computers and Operations Research, 2008. 
    }
    \end{flushleft}
  \end{textblock*}
\end{frame}

\begin{frame}
\frametitle{\textbf{Objectives}}
  \begin{itemize}[<+->]
  \item 
    Formulate the French Air Force variant of the MFMP and study its complexity.
  \item
    Build exact methods to solve the French Air Force MFMP problem.
  \item
    Expand solution methods to cope with large scale real-life MFMP problems.
  \item
    Deliver a decision making prototype for test in real-life data sets.
  \end{itemize}
\end{frame}
 
% L’objectif du projet OPTIMA est le développement de modèles permettant de répondre à
% la problématique de l’Armée de l’Air en ce qui concerne les avions de chasse. L’apport
% scientifique viendra de ces modèles et des méthodes de résolution mises en œuvre, en
% s’appuyant sur l’expertise des encadrants.

% \begin{frame}
% \frametitle{\textbf{The Military Flight and Maintenance Planning problem}}
  
%   Check Flow Balance (CFB)
%   \cite{Kozanidis2008}
%   \cite{Verhoeff2015}
%   \cite{Seif2018}  
%   \cite{Marlow2017}

%   Discrete Check and Mission (DCM)
%   \cite{Cho2011}
%   \cite{Li2016}
%   \cite{Shah2017}


%   \cite{Hahn2008}
%   \cite{Winata2011}

%   Calendar potential maintenances.

%   Slot-based maintenance.

%   The Greek: 
%   The Dutch: 


% \end{frame}

% \begin{frame}
% \frametitle{\textbf{Encoding of an MFMP solution}}

%   Patterns: \(p \in \mathcal{P}\)

%   \(p = \{a_{i0}, a_{it}, a_{it+1}, ..., a_{iT}\}\)

%   Pattern format: a solution \(x\) is represented by a mapping
%   \(f: \mathcal{I} \to \mathcal{P}\).
% \end{frame}
